\mytitile\\~

### 2019-10-13 document.tex
Table parameters

\begin{table}
	\begin{tabular}{c|c|c|c}
	Parameter & Resonator & Qubit 1 & Qubit 2\\\hline
	$\omega/2\pi$ [GHz] & 7 & 5.12 - 6.9 & 4 - 5.45\\
	$\Gamma_1$ [$\mu$s] & 0.1 & $\leq$ 10  &  $\leq$ 5\\
	$\Gamma_2$ [$\mu$s] & - & $\leq$ 7  &  $\leq$ 1
	\end{tabular}
	\caption{Device parameters}
\end{table}

>>>>

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & 250 & 250 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
\end{table}
